Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework

### 2019-04-15 paper/main.tex
Minor edits in introduction

\section{Introduction}
\label{intro}
% Broad summary of your work, come to your problem definition. 
In MIMO wireless systems, precoding matrices are used for matrix transformation of $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto the $N_T$-dimensional transmit vector, corresponding to the signal emanating out of the $N_T$ antennas of the transmitter.
The optimum precoding matrix, to achieve channel capacity via optimum power allocation is obtained via the SVD of the MIMO channel matrix. \cite{love2008overview}
The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
Hence, to avail the said benefits of SVD precoders, the receiver needs to quantize and feedback the precoders it obtains from SVD of the MIMO channel matrix.
To respect the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed only with a few single number of bits.
Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz. $2\times N_T\times N_R$ real numbers), effective quantization with just a few bits pose a significant challenge.

>>>>

\section{Introduction}
\label{intro}
% Broad summary of your work, come to your problem definition. 
In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ information vector onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating out of the $N_T$ antennas of the transmitter.
The precoding matrix used to achieve the channel capacity using optimal power allocation is obtained using the SVD of the MIMO channel matrix \cite{love2008overview}.
The MIMO channel matrix is estimated at the receiver, and the transmitter has no a-priori knowledge of the same.
Therefore, to obtain the said benefits of SVD precoders, the receiver needs to quantize and feed back the precoders it estimates from the SVD of the MIMO channel matrix.
To honour the bit budget imposed by limited feedback CSI schemes, the quantization needs to be performed using very few bits.
Given the high dimensionality of the precoders (which form a $N_T \times N_R$ complex valued matrix, viz. $2\times N_T\times N_R$ real numbers), effective quantization with just a few bits poses a significant challenge.
